---
title: "US COVID-19 Trends"
author: "By Mark Zobeck, MD, MPH"
output:
  html_document:
    df_print: paged
    toc: TRUE
    toc_float:
      collapsed: TRUE
      smooth_scroll: TRUE
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = F)
knitr::opts_chunk$set(warning = F)
knitr::opts_chunk$set(echo=FALSE) 
 
library(tidyverse)
library(readxl)
library(janitor)
library(data.table)
library(lubridate)
library(naniar)
library(knitr)
library(kableExtra)
library(ggdag)
library(randomForest)
library(brms)
library(bayesplot)
library(cowplot)
library(skimr)
library(ggthemes)
library(httr)
library(rjson)
library(jsonlite)
library(RCurl)

#time index for daily updates 
today <- format(Sys.time(), "%Y-%m-%d")
yesterday <- ymd(format(Sys.time(), "%Y-%m-%d")) - days(1)
```



```{r}
# for county level data data ------------------------------------------------------------
scrape.comp <- read_csv("https://coronadatascraper.com/timeseries-tidy.csv", 
                        col_types = "ccccdddcccd") %>% 
  mutate(date = ymd(date)) %>% 
  mutate(county = str_extract(county, ".*(?= County)")) 

#state data
states.all <- scrape.comp %>% 
  filter(country == "USA") %>% 
  filter(is.na(county))

states.counties <- scrape.comp %>% 
  filter(country == "USA") %>% 
  filter(!is.na(county))


#pop data for later
state.pop.counties <- states.counties %>% 
  distinct(state, county, population) 


# TX county data
tx.county <- scrape.comp %>% 
  filter(state == "TX" ) %>% 
  filter(!is.na(county))

#tx county cases first
tx.county.cases <- tx.county %>% 
  filter(type == "cases") %>% 
  filter(value > 0) %>% 
  group_by(county) %>% 
  mutate(since1 = rank(date))

txcounty.top10 <- tx.county.cases %>% 
  filter(date == yesterday ) %>% 
  arrange(desc(value)) %>% 
  head(10)

txcounty.top10.all <- tx.county.cases %>% 
  filter(county %in% txcounty.top10$county)


#tx county cases deaths

d1.index <- tx.county.cases %>% 
  select(county, date, since1)

tx.county.deaths <- tx.county %>% 
  filter(type == "deaths") %>% 
  left_join(d1.index)

txcounty.deaths.top10.all <- tx.county.deaths %>% 
  filter(county %in% txcounty.top10$county)

# houston data 
houston.metro <- c("Harris", "Fort Bend", "Montgomery", "Galveston", "Brazoria", "Liberty", "Chambers", "Waller")  

houston.metro.cases <- tx.county.cases %>% 
  filter(county %in% houston.metro) 

```


```{r}
# state level data --------------------------------------------------------------
states.raw <- read_csv("https://covidtracking.com/api/states/daily.csv") %>% 
  mutate(date = ymd(date)) %>% 
  mutate(death= replace(death, state == "MA" & date == "2020-03-21", 5))

state.pop <- read_xlsx("state_pop.xlsx") %>%  
  select(state = abrv, population, region)

states.pos <- states.raw %>% 
  filter(positive > 10) %>% 
  group_by(state) %>% 
  mutate(since10 = rank(date)) %>% 
  left_join(state.pop) %>% 
  mutate(pos100k = positive/population * 100000,
         death100k = death/population * 100000)



#remember this is for all states with > 10 cases only
states.top10.today <- states.pos %>% 
  filter(date == today ) %>% 
  arrange(desc(positive)) %>% 
  head(10)

states.top10.yesterday <- states.pos %>% 
  filter(date == yesterday ) %>% 
  arrange(desc(positive)) %>% 
  head(10)

if (nrow(states.top10.today) > 0) {
  states.top10 <- states.top10.today
} else {
  states.top10 <- states.top10.yesterday
}

states.top10.all <- states.pos %>% 
  filter(state %in% states.top10$state)

#top 20 for the state comparisons 
states.top20.today <- states.pos %>% 
  filter(date == today ) %>% 
  arrange(desc(positive)) %>% 
  head(20)

states.top20.yesterday <- states.pos %>% 
  filter(date == yesterday ) %>% 
  arrange(desc(positive)) %>% 
  head(20)


if (nrow(states.top20.today) > 0) {
  states.top20 <- states.top20.today
} else {
  states.top20 <- states.top20.yesterday
}

states.top20.all <- states.pos %>% 
  filter(state %in% states.top20$state)

#state new cases
states.newcases <- states.pos %>% 
  group_by(state) %>% 
  arrange(state, date) %>% 
  mutate(new.cases = ifelse(is.na(lag(positive)), -1, positive - lag(positive)),
         new.deaths = ifelse(is.na(lag(death)), -1, death - lag(death))) 

states.new.top10 <- states.newcases %>% 
  filter(state %in% states.top10$state)

states.new.top20 <- states.newcases %>% 
  filter(state %in% states.top20$state)

```

# **Welcome to US COVID-19 Trends** 
This website is intended as a reference to track US regional trends in COVID-19 cases and deaths. It uses data from [The COVID Tracking Project](https://covidtracking.com/) for state-level data and the [Corona Data Scraper](https://coronadatascraper.com/#home) for county-level data. This website does not curate the data, only reports what others are gathering. If you think there are problems with the data themselves, please route feedback to the appropriate source. If you have a question about the graphs or a suggested change in the representation of the data, then feel free to [email me](mailto: mark.zobeck@ghccpod.com). 

**Before looking at the graphs below, please read this one HUGE caution**  

#### **THESE DATA ARE WRONG**  
By that, I mean that the data are not **reality** in the sense that most people want. They **do not** tell us the **actual** number of cases and deaths per day due to COVID-19. **They are a super-dirty, extremely-noisy, very-wrong estimates.** These data come from various sources, but primarily the Departments of Health for the relevant states. There inevitably are missed cases, lags in reporting, etc, etc. For example as of the day I am writing this, the Texas DSHS reports that there are 352 COVID-19 cases in Texas, while a local news organization is reporting 826 cases. The difference comes from how cases are reported, the timeliness of updates, and the sources the news organization are drawing rom. Let this serve as an example that for every data point on the graphs below, there is untold **variability** that the graphs do not capture. **To be safe, for now assume the case numbers and deaths are wild underestimates**. As the US improves its testing capabilities, I expect these numbers to be somewhat more reliable

**If the data are so dirty, then what good is this website?**  
The utility I hope you take from this report is in looking at trends and comparisons to other states or counties. Basically, at some point you want to see the number of new cases per day go down and not up in your state. These long term trends will help people gauge the relative situation in their state compared to states that are known to be doing well or poorly. The first thing lost in the panic of a pandemic is a sense of proportion, and I hope this report give people a clearer picture of what the relevant trends are over time in their region. 

**Recap - Wrong and Right Statements about these Data**

**Wrong:** "This graph tells me there are X number of cases in my state!" (NO IT DOESN'T!)  
**Right:**  "This graph tells me there are X number of *reported* cases in my state."   

**Wrong:** "I'm concerned about this change from one day to the next day on this graph!" (TOO SHORT TO DRAW CONLCUSIONS!)  
**Right:** "I'm concerned about this trend I see *over several weeks*."  

**Wrong:** "I can extend this line I see out a week or two into future!" (MORE DISTANT FUTURE PREDICTIONS QUICKLY BECOME UNRELIABLE!)  
**Right:** "Perhaps this *long term trend* tells me something about the *next few days*."  

**Wrong:** "I am not an Epidemiologist, but I like number and, I mean, data are data so wutever. I'm going to use these graphs and post an explainer on Medium!" (PLEASE, PLEASE, PLEASE DON'T! (Unless you are indeed an infectious epidemiologist, then by all means go for it.))    
**Right:** "These are interesting pieces of information that help me understand my relative context, but *I am still going to listen to federal, state, and local advice about how to respond to COVID-19*, and I am NOT going to write an explainer on Medium."    

**Second to last disclaimer:** I myself have some training in epidemiology but am not an epidemiologist. I make no attempt here to model or predict the course of the pandemic. This is purely a descriptive project from publically available data. I will give a few thoughts below of the highlights of what I see, but I leave it to the readers to draw their own conclusions. And of course, none of this is medical advice. For relevant questions about COVID-19 precautions, testing, and treatment, contact your state or local health department. 

**Last disclaimer:** This website was last updated at **`r now()`**. I intend to update it daily. I also hope to continue to expand this website with more states and counties as time permits.

With that, I wish you happy and cautious data gazing!  
**Mark Zobeck MD, MPH**


# **States** 
A refresher about `log` scales: On the `y-axis` you will sometimes see it in `log10` scale. This makes it so that the space between 0-10, 10-100, 100-1000, and so forth are the same distance. This helps to visualize trends of things that happen explosively, like the exponential growth of a virus. I provide both an untransformed and `log10` transformed scale below.

## **The Top 10**
Here are reports for the top 10 states by reported number of cases. These are the states where COVID-19 seems to be most active. I advise that you pay attention to New York because of its current severity (what the rest of the United States could become?), and Washington and California because they had an early high case load and took earlier measures such as "social distancing" and cancelling larger gatherings, and Luisiana, which seems to have a high reported case load for its size. 

The `x-axis` below should be interpreted as "days since the state reported its 10th case". This helps to show where each state is from a standard reference point in time and facilitates better comparisons of trends. 

### Cumulative Cases For the Top 10 States by Prevalence {.tabset .tabset-fade .tabset-pills}  
#### Prevalence 
```{r states top 10}
states.top10.all %>% 
  ggplot(aes(since10, positive, group = state, color = state)) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_calc() +
  labs(y= "Reported Cases", x = "Days since reporting 10th case", color = "State") +
  ggtitle("Cumulative reported cases by days\nsince the 10th reported case.")
```

#### Log(Prevalence)
```{r}
states.top10.all %>% 
  ggplot(aes(since10, positive, group = state, color = state)) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_calc() +
  scale_y_log10() + 
  labs(y= "Logarithmic Reported Cases", x = "Days since reporting 10th case", color = "State") +
  ggtitle("Logarithmic cumulative reported cases by days\nsince the 10th reported case.")
```


### Cumulative Cases per 100,000 people For the Top 10 States by Prevalence {.tabset .tabset-fade .tabset-pills} 
These data are how many cases for every 100,000 people in the state. It helps to compare more populous states from less populous ones.  

#### Prevalence 
```{r}
states.top10.all %>% 
  ggplot(aes(since10, pos100k, group = state, color = state)) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_calc() +
  labs(y= "Reported Cases", x = "Days since reporting 10th case", color = "State") +
  ggtitle("Cumulative reported cases per 100,000 people by days\nsince the 10th reported case.")
```


#### Log(Prevalence)
```{r}
states.top10.all %>% 
  ggplot(aes(since10, pos100k, group = state, color = state)) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_calc() +
  labs(y= "Logarithmic reported Cases", x = "Days since reporting 10th case", color = "State") +
  ggtitle("Logarithmic cumulative reported cases\nper 100,000 people by days since the 10th reported case.")
```


### Cumulative Deaths For the Top 10 States by Prevalence {.tabset .tabset-fade .tabset-pills}  
#### Deaths
```{r}
states.top10.all %>% 
  ggplot(aes(since10, death, group = state, color = state)) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_calc() + 
  labs(y= "Reported Deaths", x = "Days since reporting 10th case", color = "State") +
  ggtitle("Number of cumulative reported deaths by days\nsince the 10th reported case.")

```


#### Log(Deaths)
```{r}
states.top10.all %>% 
  ggplot(aes(since10, death, group = state, color = state)) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_calc() + 
  scale_y_log10() + 
  labs(y= "Logarithmic Positive Reported Cases", x = "Days since reporting 10th case", color = "State") +
  ggtitle("Logarithmic number of cumulative reported deaths\nby days since the 10th reported case.")
```


### Cumulative Deaths per 100,000 People For the Top 10 States by Prevalence {.tabset .tabset-fade .tabset-pills}  
#### Deaths 
```{r}
states.top10.all %>% 
  ggplot(aes(since10, death100k, group = state, color = state)) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_calc() + 
  labs(y= "Reported Deaths per 100,000 people", x = "Days since reporting 10th case", color = "State") +
  ggtitle("Number of cumulative reported deaths per 100,000 people\nby days since the 10th reported case.")
```


#### Log(Deaths)
```{r}
states.top10.all %>% 
  ggplot(aes(since10, death100k, group = state, color = state)) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_calc() + 
  scale_y_log10() +
  labs(y= "Reported deaths per 100,000 people", x = "Days since reporting 10th case", color = "State") +
  ggtitle("Logarithmic number of cumulative reported deaths per 100,000 people\nby days since the 10th reported case.")

```


### New Reported Cases per Day For the Top 10 States by Prevalence {.tabset .tabset-fade .tabset-pills}  
#### New Cases 
```{r}
states.new.top10 %>% 
  ggplot(aes(since10, new.cases, group = state, color = state)) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_calc() + 
  labs(y= "New reported cases", x = "Days since reporting 10th case", color = "State") +
  ggtitle("Number of reported new cases\nby days since the 10th reported case.")
```


#### Log(New Cases)
```{r}
states.new.top10 %>% 
  ggplot(aes(since10, new.cases, group = state, color = state)) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_calc() +
  scale_y_log10() +
  labs(y= "Logarithmic daily reported cases", x = "Days since reporting 10th case", color = "State") +
  ggtitle("Logarithmic number of daily reported new cases\nby days since the 10th reported case.")
```


### News Deaths per Day For the Top 10 States by Prevalence {.tabset .tabset-fade .tabset-pills}  
#### New Deaths 
```{r}
states.new.top10 %>% 
  ggplot(aes(since10, new.deaths, group = state, color = state)) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_calc() + 
  labs(y= "New reported deaths", x = "Days since reporting 10th case", color = "State") +
  ggtitle("Logarithmic number of reported new deaths\nby days since the 10th reported case.")
```


#### Log(New Deaths)
```{r}
states.new.top10 %>% 
  ggplot(aes(since10, new.deaths, group = state, color = state)) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_calc() +
  scale_y_log10() +
  labs(y= "Logarithmic new reported deaths", x = "Days since reporting 10th case", color = "State") +
  ggtitle("Logarithmic number of reported new deaths\nby days since the 10th reported case.")
```


## **Texas**  
Focusing in on the Lone Star State. 
```{r }
the.state <- "TX"

current.state <- states.pos %>% 
  filter(state == the.state)

current.state.new <- states.newcases %>% 
  filter(state == the.state)

```

### Cumulative Cases {.tabset .tabset-fade .tabset-pills}  
#### Prevalence 
```{r }
current.state %>% 
  ggplot(aes(since10, positive, group = state, color = state)) +
  geom_line(data=states.top20.all, aes(since10, positive), color = "grey", alpha = 0.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.08, "inches"))) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_calc() +
  labs(y= "Reported Cases", x = "Days since reporting 10th case", color = "State", caption = "\nGrey arrows represent the top 20 states by reported prevalence.") +
  ggtitle("Cumulative reported cases by days\nsince the 10th reported case.")
```

#### Log(Prevalence)
```{r}
current.state %>% 
  ggplot(aes(since10, positive, group = state, color = state)) +
  geom_line(data=states.top20.all, aes(since10, positive), color = "grey", alpha = 0.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.08, "inches"))) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_calc() +
  scale_y_log10() +
  labs(y= "Logarithmic Reported Cases", x = "Days since reporting 10th case", color = "State", caption = "\nGrey arrows represent the top 20 states by reported prevalence.") +
  ggtitle("Logarithmic cumulative reported cases by days\nsince the 10th reported case.")
```


### Cumulative Cases per 100,000 People {.tabset .tabset-fade .tabset-pills} 
These data are how many cases for every 100,000 people in the state. It helps to compare more populous states from less populous ones.  

#### Prevalence 
```{r}
current.state %>% 
  ggplot(aes(since10, pos100k, group = state, color = state)) +
  geom_line(data=states.top20.all, aes(since10, pos100k), color = "grey", alpha = 0.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.08, "inches"))) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_calc()  +
  labs(y= "Reported Cases", x = "Days since reporting 10th case", color = "State", caption = "\nGrey arrows represent the top 20 states by reported prevalence.") +
  ggtitle("Cumulative reported cases per 100,000 people by days\nsince the 10th reported case.")
```


#### Log(Prevalence)
```{r}

current.state %>% 
  ggplot(aes(since10, pos100k, group = state, color = state)) +
  geom_line(data=states.top20.all, aes(since10, pos100k), color = "grey", alpha = 0.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.08, "inches"))) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_calc() +
  scale_y_log10() +
  labs(y= "Logarithmic reported Cases", x = "Days since reporting 10th case", color = "State") +
  ggtitle("Logarithmic cumulative reported cases\nper 100,000 people by days since the 10th reported case.")
```


### Cumulative Deaths {.tabset .tabset-fade .tabset-pills}  
#### Deaths
```{r}
current.state %>% 
  ggplot(aes(since10, death, group = state, color = state)) +
  geom_line(data=states.top20.all, aes(since10, death), color = "grey", alpha = 0.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.08, "inches"))) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) +
  theme_minimal_hgrid() +
  scale_color_calc()+ 
  labs(y= "Reported Deaths", x = "Days since reporting 10th case", color = "State", caption = "\nGrey arrows represent the top 20 states by reported prevalence.") +
  ggtitle("Number of cumulative reported deaths by days\nsince the 10th reported case.")

```


#### Log(Deaths)
```{r}


current.state %>% 
  ggplot(aes(since10, death, group = state, color = state)) +
  geom_line(data=states.top20.all, aes(since10, death), color = "grey", alpha = 0.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.08, "inches"))) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_calc() + 
  scale_y_log10() + 
  labs(y= "Logarithmic Positive Reported Cases", x = "Days since reporting 10th case", color = "State", caption = "\nGrey arrows represent the top 20 states by reported prevalence.") +
  ggtitle("Logarithmic number of cumulative reported deaths\nby days since the 10th reported case.")
```


### Cumulative Deaths per 100,000 People {.tabset .tabset-fade .tabset-pills}  
#### Deaths 
```{r}
current.state %>% 
  ggplot(aes(since10, death100k, group = state, color = state)) +
  geom_line(data=states.top20.all, aes(since10, death100k), color = "grey", alpha = 0.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.08, "inches"))) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) +
  theme_minimal_hgrid() +
  scale_color_calc()+ 
  labs(y= "Reported Deaths per 100,000 people", x = "Days since reporting 10th case", color = "State", caption = "\nGrey arrows represent the top 20 states by reported prevalence.") +
  ggtitle("Number of cumulative reported deaths per 100,000 people\nby days since the 10th reported case.")
```


#### Log(Deaths)
```{r}


current.state %>% 
  ggplot(aes(since10, death100k, group = state, color = state)) +
  geom_line(data=states.top20.all, aes(since10, death100k), color = "grey", alpha = 0.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.08, "inches"))) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) +
  theme_minimal_hgrid() +
  scale_color_calc() + 
  scale_y_log10()+
  labs(y= "Reported deaths per 100,000 people", x = "Days since reporting 10th case", color = "State", caption = "\nGrey arrows represent the top 20 states by reported prevalence.") +
  ggtitle("Logarithmic number of cumulative reported deaths per 100,000 people\nby days since the 10th reported case.")

```


### New Reported Cases per Day {.tabset .tabset-fade .tabset-pills}  
#### New Cases 
```{r}
current.state.new %>% 
  ggplot(aes(since10, new.cases, group = state, color = state)) +
  geom_line(data = states.new.top20, aes(since10, new.cases), color = "grey", alpha = 0.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.08, "inches"))) + 
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_calc()+ 
  labs(y= "New reported cases", x = "Days since reporting 10th case", color = "State", caption = "\nGrey arrows represent the top 20 states by reported prevalence.") +
  ggtitle("Number of reported new cases\nby days since the 10th reported case.")
```


#### Log(New Cases)
```{r}


current.state.new %>% 
  ggplot(aes(since10, new.cases, group = state, color = state)) +
  geom_line(data = states.new.top20, aes(since10, new.cases), color = "grey", alpha = 0.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.08, "inches"))) + 
  theme_minimal_hgrid() +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  scale_color_calc() +
  scale_y_log10()+
  labs(y= "Logarithmic daily reported cases", x = "Days since reporting 10th case", color = "State", caption = "\nGrey arrows represent the top 20 states by reported prevalence.") +
  ggtitle("Logarithmic number of daily reported new cases\nby days since the 10th reported case.")
```


### News Deaths by Day {.tabset .tabset-fade .tabset-pills}  
#### New Deaths 
```{r}
current.state.new %>% 
  ggplot(aes(since10, new.deaths, group = state, color = state)) +
  geom_line(data = states.new.top20, aes(since10, new.deaths), color = "grey", alpha = 0.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.08, "inches"))) + 
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_calc() + 
  labs(y= "New reported deaths", x = "Days since reporting 10th case", color = "State", caption = "\nGrey arrows represent the top 20 states by reported prevalence.") +
  ggtitle("Logarithmic number of reported new deaths\nby days since the 10th reported case.")
```


#### Log(New Deaths)
```{r}
current.state.new %>% 
  ggplot(aes(since10, new.deaths, group = state, color = state)) +
  geom_line(data = states.new.top20, aes(since10, new.deaths), color = "grey", alpha = 0.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.08, "inches"))) + 
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_calc() +
  scale_y_log10() +
  labs(y= "Logarithmic new reported deaths", x = "Days since reporting 10th case", color = "State", caption = "\nGrey arrows represent the top 20 states by reported prevalence.") +
  ggtitle("Logarithmic number of reported new deaths\nby days since the 10th reported case.")
```



# **Counties**  
Note that instead of days since 10th case, the `x-axis` is not days since reported 1st case.   

## **Texas**    
### Cumulative Cases per Day for the Top 10 Counties {.tabset .tabset-fade .tabset-pills}  
#### Prevalence 
```{r}
txcounty.top10.all %>% 
  ggplot(aes(since1, value, group = county, color = county)) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_tableau()+ 
  labs(y= "Reported cases", x = "Days since reporting 1st case", color = "County") +
  ggtitle("Cumulative reported cases\nby days since the 1st reported case.")
```


#### Log(New Cases)
```{r}
txcounty.top10.all %>% 
  ggplot(aes(since1, value, group = county, color = county)) +
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_tableau()+ 
  scale_y_log10()+
  labs(y= "Logarithmic reported cases", x = "Days since reporting 1st case", color = "County") +
  ggtitle("Logarithmic cumulative reported cases\nby days since the 1st reported case.")
```



# **Houston Metro Area**  
### Cumulative Cases For the Houston Metro Area {.tabset .tabset-fade .tabset-pills}    
#### Prevalence 
```{r}
houston.metro.cases %>% 
  ggplot(aes(since1, value, group = county, color = county)) +
  geom_line(data = txcounty.top10.all, aes(since1, value), color = "grey", alpha = 0.8, arrow = arrow(angle = 15, type = "closed", length = unit(0.08, "inches"))) + 
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_tableau() +
  labs(y= "Reported cases", x = "Days since reporting 1st case", color = "County", caption = "\nGrey arrows represent the top 10 counties by reported prevalence.") +
  ggtitle("Cumulative reported cases\nby days since the 1st reported case.")
```


#### Log(Prevalence)
```{r}
houston.metro.cases %>% 
  ggplot(aes(since1, value, group = county, color = county)) +
  geom_line(data = txcounty.top10.all, aes(since1, value), color = "grey", alpha = 0.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.08, "inches"))) + 
  geom_line(alpha = 0.7, size = 1.5, arrow = arrow(angle = 15, type = "closed", length = unit(0.1, "inches"))) + 
  theme_minimal_hgrid() +
  scale_color_tableau() +
  scale_y_log10() + 
  labs(y= "Logarithmic reported cases", x = "Days since reporting 1st case", color = "County", caption = "\nGrey arrows represent the top 10 counties by reported prevalence.") +
  ggtitle("Logarithmic Cumulative reported cases\nby days since the 1st reported case.")
```


